\cvsection{TECHNICAL PROJECTS AND ACHIEVEMENTS}
\cvevent{}{CyBrics CTF 2019 | InfoSecIITR}{July 2019 and Septmenber 2019}{}
\begin{itemize}
\item CyBrics CTF was a world-level jeopardy style CTF arganized by the CyBrics team in July. The initial qualifying round was held in July where 5 teams from each participating country(BRICS) would qualify for an attack defence style finals.
\item Part of the team inv4ision which qualified for the finals in Vadodara, Gujarat
\item Placed in top 20 position in the attack-defence final.
\end{itemize}
\divider

\cvevent{}{CTF  | InfoSecIITR}{August 2018 -- Present}{}
\begin{itemize}
\item Participated in multiple CTFs as part of the team InfoSecIITR.
\item Won many CTFs like CSAW India, CodeFest CTF, HackTM Quals, HackIM Quals, Whitehat CTF.
\item  Part of the organising team of a worldwide CTF Backdoor CTF-2019.
\end{itemize}
\divider


\cvevent{}{Omniport infrastructure, core and services | IMG, IIT-R}{August 2019 -- present}{}
\begin{itemize}
\item Omniport is a platform for institutes to deploy their portal
(like Channel i for IIT Roorkee), by and for the students.
\item Omniport is completely generic, but offers varying levels of customisability, to suit the needs of any institute worldwide.
\item Contributed to the the Django backend and React frontend including core and services.
\item Tech stack includes JS, ReactJS, Redux, Python, Django, Docker.
\item Visit https://omniport.readthedocs.io.
\end{itemize}
\divider

\cvevent{}{Presence | IMG, IIT-R}{March 2019 -- present}{}
\begin{itemize}
\item Presence is a utility tool used inside the IMG lab to track the lab time of people.
\item It also tells us about the people present in the lab at any time using a simple slackbot query.
\item Contributed to the client side script which updates the presence backend about the members present. Also contributed to the deployment of the client side on a raspberry pi.
\item Tech stack includes python, Django, Docker and cron.
\item Visit https://github.com/rish9101/presence\_docker/tree/rishi\_presence
\end{itemize}
\divider